REDO Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution I: Methods and Test Case

### 2017-11-21 main.tex
through 2.5.6

We assume the FUV luminosity for each our stars is everywhere optically thin. The FUV flux in each cell is summed over contributions from each star. We parameterize the local photoelectric heating rate following \citet{BakesTielens1994}, \citet{Wolfire2003}, and \citet{Bergin2004}, where 
\begin{equation}
\label{eq:PE}
\Gamma_{\rm pe} = 1.3 \times 10^{-24} \epsilon n_{\rm H} G_{\rm eff} D \left[{\rm erg~s~cm^{-3}}\right]
\end{equation}
where $\epsilon$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\rm{exp}(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust to gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}. Aside from a different treatment of $D$ and the attenuation, both discussed below, this is equivalent to the method used in \citet{Hu2016} and \citet{Hu2017}.

$D$ is computed consistently with our \texttt{Grackle} dust model, using the broken power law fit from \citet{Remy-Ruyer2014} (see Section~\ref{sec:chemistry}). The extremely low dust to gas ratio in our modeled galaxies leads to a reduction in the photoelectric heating rate by approximately two orders of magnitude, as compared to a model that assumes a $D$ that scales linearly with metallicity at very low metallicity. At these low metallicities, the FUV field only becomes optically thick at length scales of $\sim$ 100 pc for densities of $n \sim 10^2$ \ccunit. Given that the ambient density of the ISM is generally 1 - 10 cm$^{-3}$, we can safely assume the FUV field to be optically thin. However, we do include a localized attenuation prescription which may influence high density or metal enriched regions of the galaxy. We approximate $N_{\rm H}$ given in the equation above locally, as $n_{\rm H}\Delta x$, where $\Delta x$ is the cell width; this approximation is necessarily resolution dependent, but substantially more computationally efficient than direct ray tracing.

Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density ($n_e$). This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations; each of which are not followed directly in these simulations. Instead, we use a log-linear fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$. %This is a compromise between adoption a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equillibrium chemistry \citet[e.x.][]{Hu2016}.

>>>>

%mm We assume the FUV luminosity for each our stars is everywhere optically thin. The 
     We assume the galaxy is mostly optically thin to stellar FUV.  Therefore, the stellar
%
FUV flux in each cell is summed over the contributions from each star
%mm 
   with a local approximation to the attenuation within dense cells applied. 
We parameterize the local photoelectric heating rate \citep{BakesTielens1994,Wolfire2003,Bergin2004}
\begin{equation}
\label{eq:PE}
\Gamma_{\rm pe} = (1.3 \times 10^{-24} \mbox{~erg~s~cm}^{-3}) \epsilon n_{\rm H} G_{\rm eff} D 
\end{equation}
where $\epsilon$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\rm{exp}(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust to gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}. Aside from a different treatment of $D$ and the attenuation, both discussed below, this is equivalent to the method used in \citet{Hu2016,Hu2017}.

$D$ is computed consistently with our \texttt{Grackle} dust model, using the broken power law fit from \citet{Remy-Ruyer2014}, as described in Section~\ref{sec:chemistry}. The extremely low dust to gas ratio in our modeled galaxies leads to a reduction in the photoelectric heating rate by approximately two orders of magnitude, as compared to a model that assumes a $D$ that scales linearly with metallicity at very low metallicity. At these low metallicities, the FUV field only becomes optically thick at length scales of $\sim$ 100 pc for densities of $n \sim 10^2$~\ccunit. Given that the ambient density of the ISM is generally 1--10~cm$^{-3}$, we can safely assume the FUV field to be optically thin. However, we do include a localized attenuation prescription that may influence high-density or metal-enriched regions of the galaxy. We approximate $N_{\rm H}$ given in the equation above locally, as $n_{\rm H}\Delta x$, where $\Delta x$ is the cell width; this approximation is necessarily resolution dependent, but substantially more computationally efficient than direct ray tracing.

Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density $n_e$. This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations; none of which are followed directly in these simulations. Instead, we use a log-linear fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$. %This is a compromise between adoption a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equillibrium chemistry \citet[e.x.][]{Hu2016}.
